% Interesting trick to instead make the chapter number the letter A for this appendix.
\begingroup
\renewcommand\thechapter{A}
\titleformat{\chapter}[display]
{\normalfont\huge\bfseries}{}{20pt}{\Huge}
\setcounter{section}{0} % Set the section counter back to 0 so earlier chapters don't interfere.
\setcounter{figure}{0} % Set the figure counter back to 0 so earlier figures don't interfere.

\chapter*{Appendix A - Windows Subsystem for Linux}
\addcontentsline{toc}{chapter}{Appendix A - Windows Subsystem for Linux}
\markboth{Appendix A}{}

As of TensorFlow 2.10's release in September 2022, Windows is no longer natively supported with GPU access \autocite{tensorflow_install_nodate}.
To circumvent this issue, the official TensorFlow Docker container can be pulled and used on a Windows host \autocite{tensorflow_install_nodate-1}.
Docker aims to mitigate issues of software incompatibility across devices through containers, which act similarly to virtual machines 
in that they emulate another system with the necessary dependencies on a host. In this specific case, Docker uses the Windows Subsystem for 
Linux to virtualize an Ubuntu client that supports TensorFlow's latest releases with GPU support.

\para \textbf{I'm not going to remove this section until I make a final decision on the following:}
\begin{itemize}
    \item My RTX 3060 Ti seems to work at the same speed, if not slower, than a Colab GPU.
    \item My CPU works over 1000x faster than both, but my research shows that this is true for small datasets and the time needed grows exponentially.
    \item It is possible that the GPU speed issues are due to low VRAM allocation, but this cannot actually be resolved without \textbf{DUAL-BOOTING LINUX.}
    \item Though, is that even necessary? Tensorflow 2.10 is a version that supports the 3060Ti. If half of the things online use completely outdated 
    Python versions, why shouldn't I use a slightly outdated TensorFlow version?
    \item All in all, the decision between Colab and local use will depend entirely on the size of the chosen dataset, though it's likely Colab will win 
    out. 
\end{itemize} 